Survey paper tables and figures

### 2021-09-17 indicators/paper/responses-to-reviews.tex

\section*{Reviewer 1}

\begin{quote}
  In section 1.B, you mention non-trivial signal processing and direct the
  reader to github to learn more. I would like to see more discussion of how
  each source was processed. If this is not possible due to length constraints,
  where can the reader find more details? Is there documentation at the Delphi
  website that explains how the data from each source is processed? In a quick
  search at the Delphi website, I was not able to find information about how the
  survey data (for example) were weighted. These details will be important to
  those using the data.
\end{quote}
Thanks, this is an important point. We have added a sentence to Section 1.B to
make clear that detailed documentation, including such details as the survey
weighting procedures and the day-of-week adjustments used in other data sources,
is available on the public documentation site.

\section*{Reviewer 2}

\begin{quote}
  This paper describes a diverse public database of signals related to COVID-19
  prevalence, including symptom survey data, mobility, at-home tests, and
  hospitalizations. The database is unique, important, and useful, especially in
  the current surveillance-limited context of the United States. However, the
  main analyses presented in the results section did not feel cohesive, and the
  ``story'' of the paper felt incomplete. While I respect the challenge of
  dividing work among multiple related papers, I think that a key goal of
  revisions might be to add further independent analyses of the data described
  that emphasize its utility beyond comparisons to cases or add additional
  analyses to build a unique cohesive story for this paper.
\end{quote}
We appreciate this point and agree the message may have gotten split among
manuscripts unnecessarily. We have made some changes to the Results section
accordingly. Most notably, we have replaced Figure 6 with one that more clearly
shows a potential use case of the data presented beyond forecasting of cases; it
now shows how data sources in the API could have aided in planning for the COVID
vaccination campaign.

@@

\begin{quote}
  The strength of observed correlations change (non-monotonically) over time,
  and the implications of this are not discussed.
\end{quote}
While it is difficult to fully explain the changes in correlation---they are
likely due to a variety of changes in reporting practices, health-seeking
behavior, survey response patterns, and so on---one key point is that the
strength of the correlation depends on the overall differences between counties.
That is, if counties have very similar COVID case rates, it is difficult to
achieve a high Spearman correlation between case rates and signals, because
getting the rank correct is difficult. If counties have widely varying COVID
case rates, a signal that provides information about cases will be able to
achieve a higher Spearman correlation.

We have slightly expanded our discussion of Figure 2 to make this point, though
we have tried to keep the discussion brief so as not to sidetrack the main
discussion of the manuscript.

\begin{quote}
  Signal strength is compared only to cases (rather than downstream outcomes
  like hospitalization or death).
\end{quote}
We have extended the Supplementary Information to include more detailed
comparisons between our signals and reported COVID hospitalizations, including
comparisons of correlations. These show broadly similar results as the COVID
case analyses. Section 2.B now points to the Supplement for interested readers
to examine these analyses.

\begin{quote}
  The case studies of signal utility that are provided seem stylized.
  Policymakers would *know* in real-time when backlogged cases are reported and
  can adjust case numbers accordingly or when cases are not being reported due
  to holiday backlogs.
\end{quote}
Unfortunately this is not the case: Backlogs and reporting delays are generally
poorly understood and can happen unexpectedly, and users of these datasets often
have to make informed guesses about changes. For instance, many backlogs are due
to retrospective audits of records that uncover cases and deaths that were
incorrectly classified, and can affect case and death estimates months in the
past. Until the audits are complete, policymakers would not know about the
corrections, their magnitude, or the effects they'd have on policy decisions.

### 2021-09-17 survey/code/paper-tables.Rmd
WIP Figure 2 reimplementation in R

```{r setup, message=FALSE}
library(data.table)
library(dplyr)
library(tidyr)
library(epitools)
library(tidycensus)

@@

>>>>

```{r setup, message=FALSE}
library(data.table)
library(dplyr)
library(tidyr)
library(epitools)
library(tidycensus)
library(zoo)

@@

## Trends in each signal, by Census region

```{r fetch-signal-data}
start_day <- "2020-04-06"
end_day <- "2021-04-05"

anosmia <- data %>%
  mutate(date = as.Date(StartDatetime),
         anosmia = is_selected(B2, "13"),
         state = toupper(name_to_abbr(state_fips_to_name(fips)))) %>%
  group_by(date, state) %>%
  summarize(anosmia = weighted.mean(anosmia, weight, na.rm = TRUE)) %>%
  select(time_value = date, value = anosmia, geo_value = state) %>%
  as.covidcast_signal(signal = "anosmia")

signals <- covidcast_signals(
  c("fb-survey", "fb-survey", "jhu-csse", "hhs", "jhu-csse"),
  c("raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
    "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  start_day, end_day,
  geo_type = "state") %>%
  aggregate_signals(format = "long")

signals <- append(signals, anosmia)

signals$signal <- factor(
  signals$signal,
  levels = c("anosmia", "raw_wcli", "raw_whh_cmnty_cli", "confirmed_incidence_prop",
             "confirmed_admissions_covid_1d_prop", "deaths_incidence_prop"),
  labels = c("Anosmia %", "CLI %", "Community CLI %", "Cases per 100,000",
             "Hospitalizations per 100,000", "Deaths per 100,000"))

to_plot <- signals %>%
  mutate(geo_value = toupper(geo_value)) %>%
  inner_join(select(state_census, ABBR, REGION, POPESTIMATE2019),
             by = c("geo_value" = "ABBR")) %>%
  group_by(REGION, time_value, signal) %>%
  summarize(value = weighted.mean(value,
                                  ifelse(data_source %in% c("jhu-csse", "hhs"),
                                         POPESTIMATE2019, sample_size),
                                  na.rm = TRUE))

to_plot <- to_plot %>%
  group_by(REGION, signal) %>%
  arrange(time_value) %>%
  mutate(value = rollmean(value, 7, fill = NA))

ggplot(to_plot, aes(x = time_value, y = value, color = REGION)) +
  geom_line() +
  facet_wrap(vars(signal), nrow = 2, ncol = 3, scales = "free_y") +
  labs(x = "Date", y = "Value") +
  scale_x_date(date_breaks = "3 months",
               date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  theme_bw() +
  theme(legend.position = "bottom")
```
